---
title: "EC"
author: "YL"
format: html
editor: visual
---

```{r}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  echo = FALSE
)
```

```{r}
# Load library here
library(dplyr)
library(readr)
library(tidyr)
library(knitr)
library(kableExtra)
```

# Introduction

Maisha's part

# Methodology

```{r}
# Data Preparation
original_df <- read_csv("Data/electric-car-sales-share/electric-car-sales-share.csv")

countries <- selected_countries <- c("China", "India", 
                                     "Japan", "Austria", 
                                     "Finland", "Norway")

cleaned_df <- original_df %>%
  rename(Country = Entity,
         Electric_Car_Share = `Share of new cars that are electric`) %>%
  filter(Year >= 2013, Year <= 2023, 
         Country %in% countries) %>%
  drop_na()

```

The data has `r ncol(cleaned_df)` observations and `r nrow(cleaned_df)` variables. There are three numeric variables (Year and Electric_car_share) and two character variable (Country and Code). The description of each variable is provided in @tbl-DataDict.

```{r}
# Preparation for data descriptions table
data_description <- data.frame(
  Variable = c("Country", "Code", "Year", "Electric_Car_Share"),
  Description = c(
    "Name of the country where the data was collected",
    "ISO 3-letter country code",
    "Year of observation (from 2013 to 2023)",
    "Percentage of electric vehicles in new car sales"
  ))
```

```{r}
#| label: tbl-DataDict
#| tbl-cap: "Data dictionary for electric car sales share dataset"

data_description %>%
  kable(escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped",
                                      "hover",
                                      "condensed",
                                      "responsive",
                                      "bordered"),
                full_width = FALSE,
                position = "center")

```

# Disucussion and Visualisations

Yao's part

# Conclusion and Recommendation

Xinly's part
